Simple and robust inference of connectomes using partial correlation coefficients

### 2014-06-11 article.tex
detailed

Finally since there is a high correlation between neurons, we made a
low-rank hypothesis and perform noise filtering through a principal component
approach. From the $p$ eigen vectors, we only kept $80\%$ of
the eigen vectors which have the largest eigen value. In the context of the
challenge, this assumption was deduced from ground truth of provided network.

@@

% Speak about why averaging
The quality of the signal filtering and network inference is dependent upon
good hyper-parameter selection, which are themselves dependent on the properties
of the targeted network and measurement conditions, e.g. signal to noise ratio.
Ensemble methods are known to improve robustness with respect to parameter
selection [todo cite] and improve performance [todo cite].
A weighted average $y_{stack}$ of partial correlation matrices was made
by varying uniformly the hard-threshold value (parameter $\tau$) and the design
of the low-pass filter (coefficients $c_l$). The stacked connectivity score
matrix $y_{stacking}$ is given by
\begin{align}
y_{stack} =  \dfrac{1}{\sum_{k\in\{1,..,4\}} w_k |T_k|} \sum_{k=1}^{k=4}  w_k \sum_{q \in T_k} G^{q,k}(X_t^i)
\end{align}
where $f(X, k, \tau)$ gives the predicted adjacency matrix, i.e. applies the
filtering and inference methodologies (as described
in sections \ref{sec:filter} and \ref{sec:inference}), with a  given value
$\tau$ for the hard-threshold among a set of thresholds $T_k$ of size $|T_k|$
and the $k^{th}$ low-pass filter pattern associated to a weight $w_k$ whose
values are $w_1 = 0.01 , w_2 =1, w_3 = 0.7, w_4 = 0.9$.

>>>>

Finally since there is a high correlation between neurons, we made a
low-rank hypothesis and perform noise filtering through a principal component
analysis. From the $p$ eigen vectors, we only kept $80\%$ of
the eigen vectors which have the largest eigen value. In the context of the
challenge, this assumption was deduced from ground truth of provided network.

@@

% Speak about why averaging
The quality of the signal filtering and network inference is dependent upon
good hyper-parameter selection, which are themselves dependent on the properties
of the targeted network and measurement conditions, e.g. signal to noise ratio.
Ensemble methods are known to improve robustness with respect to parameter
selection [todo cite] and improve performance [todo cite].
A weighted average $y_{stack}$ of partial correlation matrices was made
by varying uniformly the hard-threshold value (parameter $\tau$) and the design
of the low-pass filter (coefficients $c_l$). The stacked connectivity score
matrix $y_{stack}$ is given by
\begin{align}
y_{stack} =  \dfrac{1}{\sum_{k\in\{1,..,4\}} w_k |T_k|} \sum_{k=1}^{k=4}  w_k \sum_{q \in T_k} G^{q,k}(X_t^i)
\end{align}
where $f(X, k, \tau)$ gives the predicted adjacency matrix, i.e. applies the
filtering and inference methodologies (as described
in sections \ref{sec:filter} and \ref{sec:inference}), with a  given value
$\tau$ for the hard-threshold among a set of thresholds $T_k$ of size $|T_k|$
and the $k^{th}$ low-pass filter pattern associated to a weight $w_k$ whose
values are $w_1 = 0.01 , w_2 =1, w_3 = 0.7, w_4 = 0.9$.
